Validating Cell Tower Clustering for Mobility Prediction

### 2012-12-12 docs/paper589.tex
More changes.

@@

In this project, we analyze one published algorithm for oscillation detection \cite{mobilityprofiler} and evaluate its performance using GPS data as ground-truth.

\xxx{``In the next section, we describe....''}
\xxx{More about the results.}

@@

\section{Methodology}

\xxx{What were our methods?\\- Implemented clustering algorithm. Explain mobility paths, oscillations, oscillation graph etc. \\- RM. We sampled the RM dataset and compared it to
the Nokia MDC \\- MDC. We apply the oscillation clustering to the MDC and look at the position
characteristics of the clusters.}

@@

\section{Results}

\xxx{Results introduction fluff.}

@@

\section{Conclusion}

We have evaluated a clustering algorithm used to eliminate the oscillation effect in cellular mobility prediction. Our main contribution is the use of GPS data to evaluate if the clustered towers are geographically close to each other, which would be circumstantial evidence in favor of the clustering algorithm. We find that the clustering algorithm proposed in \cite{mobilityprofiler} performs well on the two metrics we define, cluster distance and cluster incompleteness.

@@

\bibliographystyle{plain}
\bibliography{eecs589Report}

>>>>

\xxx{Abstract}

@@

In this project, we analyze one published algorithm for oscillation detection \cite{mobilityprofiler} and evaluate its performance using GPS data as ground-truth. We find that this algorithm performs surprisingly well as measured by two metrics we define.

This report is structured as follows. In the next section, we motivate our work by explaining why clustering validation is important. In section~\ref{sec:methodology} we describe our methodology  and explain the algorithm we will evaluate. We present and discuss results in section~\ref{sec:results}, and conclude in section~\ref{sec:conclusion}.
\xxx{More about the results.}

@@

\section{Methodology}
\label{sec:methodology}
\xxx{What were our methods?\\- Implemented clustering algorithm. Explain mobility paths, oscillations, oscillation graph etc. \\- RM. We sampled the RM dataset and compared it to
the Nokia MDC \\- MDC. We apply the oscillation clustering to the MDC and look at the position
characteristics of the clusters.}

@@

\section{Results}
\label{sec:results}
\xxx{Results introduction fluff.}

@@

\section{Conclusion}
\label{sec:conclusion}
We have evaluated a clustering algorithm used to eliminate the oscillation effect in cellular mobility prediction. Our main contribution is the use of GPS data to evaluate if the clustered towers are geographically close to each other, which would be circumstantial evidence in favor of the clustering algorithm. We find that the clustering algorithm proposed in \cite{mobilityprofiler} performs well on the two metrics we define, cluster distance and cluster incompleteness.

@@

\bibliographystyle{IEEEtranS}
\bibliography{eecs589Report}
